---
title: CV
name: Fei
surname: Gu
position: "Ph.D Student"
address: "Institute of Psychology, Chinese Academy of Sciences"
www: flashsherlock.github.io
email: "guf@psych.ac.cn"
orcid: 0000-0001-7253-9097
github: flashsherlock
googlescholar: iMfym1QAAAAJ
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%m-%d-%Y')`"
csl: apa-cv.csl # change this if you want to use other citation styles
# biblio-style: apa
output: 
  vitae::awesomecv:
    # citation_package: biblatex
    keep_tex: true
    pandoc_args: ["--lua-filter=lua/strong.lua"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Institution,
  ~ Where,
  "PhD Student, Cognitive Neuroscience",
  "Advisor: Dr. Wen Zhou",
  "09/2019-present",
  "Institute of Psychology, Chinese Academy of Sciences",
  "Beijing, China",
  "Bachelor of Science, Psychology, Minor in Biology",
  "Thesis: Implicit Acquisition of Odor Valence",
  "09/2015-07/2019",
  "Beijing Normal University",
  "Beijing, China",
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution,
    where = Where,
    why = Advisor
  )
```

# Awards and Grants

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Institution,
  ~ Supp,
  ~ Amount,
  '2020', "Merit Student","Chinese Academy of Sciences",NA,NA,
  '2019', "Student's Innovation Training Program","Chinese Academy of Sciences",NA,'$1500',
  '2019', "Excellent Graduate","Beijing Municipal Education Commission",NA,NA,
  '2019', "Beisen Scholarship","Beijing Beisen Cloud Computing Co Ltd",NA,'$150',
  '2019', "Academic Scholarship","Beijing Normal University",NA,'$150',
  '2017-2018', "Competition Scholarship","Beijing Normal University",NA,'$670',
  '2018', "Hornorable Mention at The Interdisciplinary Contest in Modeling","The Consortium for Mathematics and its Applications (COMAP)",NA,NA,
  '2017', "Bronze Medal at the iGEM 2017 Competition","International Genetically Engineered Machine (iGEM) Foundation",NA,NA,
  '2016', "Beijing Student's Innovation and Entrepreneurship Training Program","Beijing Municipal Education Commission",NA,'$1500',
  '2016-2018', "Jingshi Scholarship","Beijing Normal University",NA,'$1950',
) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```

# Research Interests
\vspace{1.5mm}
Olfaction; amygdala; odor representation; fMRI

# Research Experience

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Institution,
  ~ Supp,
  ~ Amount,
  '2019-present', "Doctoral Researcher","Institute of Psychology, Chinese Academy of Sciences",
  list("Topic: Odor representations in the amygdala","Advisor: Dr. Wen Zhou"),NA,
  '2017-2018', "Research Assistant","Faculty of Psychology, Beijing Normal University",
  list("Topic: Child temperament","Advisor: Dr. Xuemei Lei"),NA,
  '2016-2017', "Research Assistant","Faculty of Psychology, Beijing Normal University",
  list("Topic: The spatial-numerical association of response codes (SNARC) effect","Advisor: Dr. Ting Jiang"),NA
) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```

# Research Outputs
\vspace{1.5mm}
## Articles

```{r}
bibliography_entries("Prepare.bib")
# bibliography_entries("Publication.bib") %>% dplyr::arrange(desc(issued))
# output one by one to increace line space
all <- bibliography_entries("Publication.bib") %>% dplyr::arrange(desc(issued))
all[1,]
all[2,]
# for (i in nrow(all)) {
#   rmarkdown::render(all[i,])
# }
```

## Presentations

```{r}
# bibliography_entries("Presentations.bib") %>% dplyr::arrange(desc(issued))
pre <- bibliography_entries("Presentations.bib") %>% dplyr::arrange(desc(issued))
pre[2,]
pre[3,]
```

# Teaching Experience

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Institution,
  ~ Supp,
  ~ Amount,
  '2018', "Cognitive Psychology","Beijing NO.4 High School",NA,NA,
  '2018', "Introduction to Psychology","Hailin Senior High School",NA,NA
) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```

# Professional Activities
\vspace{1.5mm}
## Reviewer

- The Innovation
- 2023 International Annual Conference on Complex Systems and Intelligent Science

## Membership

- Chinese Psychological Society
