%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Fei}{Gu}

\position{Ph.D Student}
\address{Institute of Psychology, Chinese Academy of Sciences}

\email{\href{mailto:guf@psych.ac.cn}{\nolinkurl{guf@psych.ac.cn}}}
\homepage{flashsherlock.github.io}
\orcid{0000-0001-7253-9097}
\googlescholar{iMfym1QAAAAJ}
\github{flashsherlock}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {04-07-2024}
    {Fei Gu~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\section{Education}\label{education}

\begin{cventries}
    \cventry{PhD Student, Cognitive Neuroscience}{Institute of Psychology, Chinese Academy of Sciences}{Beijing, China}{09/2019-present}{\begin{cvitems}
\item Advisor: Dr. Wen Zhou
\end{cvitems}}
    \cventry{Bachelor of Science, Psychology, Minor in Biology}{Beijing Normal University}{Beijing, China}{09/2015-07/2019}{\begin{cvitems}
\item Thesis: Implicit Acquisition of Odor Valence
\end{cvitems}}
\end{cventries}

\section{Awards and Grants}\label{awards-and-grants}

\begin{cventries}
    \cventry{Chinese Academy of Sciences}{Merit Student}{2020}{}{}\vspace{-4.0mm}
    \cventry{Chinese Academy of Sciences}{Student's Innovation Training Program}{2019}{\$1500}{}\vspace{-4.0mm}
    \cventry{Beijing Municipal Education Commission}{Excellent Graduate}{2019}{}{}\vspace{-4.0mm}
    \cventry{Beijing Beisen Cloud Computing Co Ltd}{Beisen Scholarship}{2019}{\$150}{}\vspace{-4.0mm}
    \cventry{Beijing Normal University}{Academic Scholarship}{2019}{\$150}{}\vspace{-4.0mm}
    \cventry{Beijing Normal University}{Competition Scholarship}{2017-2018}{\$670}{}\vspace{-4.0mm}
    \cventry{The Consortium for Mathematics and its Applications (COMAP)}{Hornorable Mention at The Interdisciplinary Contest in Modeling}{2018}{}{}\vspace{-4.0mm}
    \cventry{International Genetically Engineered Machine (iGEM) Foundation}{Bronze Medal at the iGEM 2017 Competition}{2017}{}{}\vspace{-4.0mm}
    \cventry{Beijing Municipal Education Commission}{Beijing Student's Innovation and Entrepreneurship Training Program}{2016}{\$1500}{}\vspace{-4.0mm}
    \cventry{Beijing Normal University}{Jingshi Scholarship}{2016-2018}{\$1950}{}\vspace{-4.0mm}
\end{cventries}

\section{Research Interests}\label{research-interests}

\vspace{1.5mm}

Olfaction; amygdala; odor representation; fMRI

\section{Research Experience}\label{research-experience}

\begin{cventries}
    \cventry{Institute of Psychology, Chinese Academy of Sciences}{Doctoral Researcher}{2019-present}{}{\begin{cvitems}
\item Topic: Odor representations in the amygdala
\item Advisor: Dr. Wen Zhou
\end{cvitems}}
    \cventry{Faculty of Psychology, Beijing Normal University}{Research Assistant}{2017-2018}{}{\begin{cvitems}
\item Topic: Child temperament
\item Advisor: Dr. Xuemei Lei
\end{cvitems}}
    \cventry{Faculty of Psychology, Beijing Normal University}{Research Assistant}{2016-2017}{}{\begin{cvitems}
\item Topic: The spatial-numerical association of response codes (SNARC) effect
\item Advisor: Dr. Ting Jiang
\end{cvitems}}
\end{cventries}

\section{Research Outputs}\label{research-outputs}

\vspace{1.5mm}

\subsection{Articles}\label{articles}

\phantomsection\label{refs-624944ee6e93d95d4b7cd55853f78f6c}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Gu_valence_2024}
\textbf{Gu, F.}, Yun, H., Chen, W., \& Zhou, W. (n.d.). \emph{Entwined
codes of odor pleasantness and facial affect below awareness}.

\end{CSLReferences}

\phantomsection\label{refs-8dd4cf85c1fe132edf6526a1eb3da8bd}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-shan2023neural}
Shan, L., Yuan, L., Zhang, B., Ma, J., Xu, X., \textbf{Gu, F.}, Jiang,
Y., \& Dai, J. (2023). Neural integration of audiovisual sensory inputs
in macaque amygdala and adjacent regions. \emph{Neuroscience Bulletin},
\emph{39}(12), 1749--1761.

\end{CSLReferences}

\phantomsection\label{refs-4e2356d0f68c573869fb2c3d757cff6e}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-shan2022mapping}
Shan, L., Huang, H., Zhang, Z., Wang, Y., \textbf{Gu, F.}, Lu, M., Zhou,
W., Jiang, Y., \& Dai, J. (2022). Mapping the emergence of visual
consciousness in the human brain via brain-wide intracranial
electrophysiology. \emph{The Innovation}, \emph{3}(3).

\end{CSLReferences}

\subsection{Presentations}\label{presentations}

\phantomsection\label{refs-a6103ad59703c9ce34569450f5e90894}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Gu_brownbag_2023}
\textbf{Gu, F.}, Yuan, L., Zhou, W., \& Dai, J. (2023, October).
\emph{Odor-specific oscillatory response profiles in the macaque
amygdala}. {[}Talk session{]}. Brown Bag Series in the State Key
Laboratory of Brain and Cognitive Science. Beijing, China.

\end{CSLReferences}

\phantomsection\label{refs-6db8de78c1b7b9f933a8afcd4e1bec59}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Gu_ucas_2019}
\textbf{Gu, F.}, Chen, W., \& Zhou, W. (2019, November).
\emph{Interaction between olfactory and visual valence in the amygdala}.
{[}Talk session{]}. University of Chinese Academy of Sciences. Beijing,
China.

\end{CSLReferences}

\section{Teaching Experience}\label{teaching-experience}

\begin{cventries}
    \cventry{Beijing NO.4 High School}{Cognitive Psychology}{2018}{}{}\vspace{-4.0mm}
    \cventry{Hailin Senior High School}{Introduction to Psychology}{2018}{}{}\vspace{-4.0mm}
\end{cventries}

\section{Professional Activities}\label{professional-activities}

\vspace{1.5mm}

\subsection{Reviewer}\label{reviewer}

\begin{itemize}
\tightlist
\item
  The Innovation
\item
  2023 International Annual Conference on Complex Systems and
  Intelligent Science
\end{itemize}

\subsection{Membership}\label{membership}

\begin{itemize}
\tightlist
\item
  Chinese Psychological Society
\end{itemize}



\end{document}
