---
output: html_document
title: "Plots for monkeys"
author: "Fei"
date: "`r Sys.time()`"
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, cache = F,tidy = F,
fig.align='center',fig.showtext=TRUE,results="hold",fig.show = "hold")
library(bruceR)
library(psych)
library(RColorBrewer)
library(ggpubr)
library(ggrepel)
library(R.matlab)
library(ggprism)
library(sysfonts)
library(pheatmap)
library(mlr3verse)
library(randomForest)
library(rpart.plot)
library(abind)
library(purrr)
library(foreach)
library(doParallel)
font_add("Helvetica", "Helvetica.ttc")
theme_set(theme_prism(base_size = 9,
                      base_family = "Helvetica",
                      base_fontface = "plain",
                      base_line_size = 0.5,
                      base_rect_size = 0.5,))
# theme_update(text = element_text(family = "Helvetica",
#                                  face = "plain", size = 9))
lgr::get_logger("mlr3")$set_threshold("warn")
# progress bar
progressr::handlers(global = TRUE)
progressr::handlers("progress")
```

# settings and functions
```{r}
# settings
colors <- c(
    "#777DDD", "#69b4d9", "#149ade", "#41AB5D", "#ECB556",
    "#000000", "#E12A3C", "#777DDD", "#41AB5D", "#DE7B14"
)
# roi levels
roi_level <- c("BA","BM","La","CoA","CeMe","Hi","S")
cmap <- c("#D95319", "#EDB120", "#7E2F8E", "#0072BD")
odors <- c("Ind", "Iso_l", "Iso_h", "Peach", "Banana", "Air", "Odor")
monkeys <- c("RM033", "RM035", "2monkey")
root_dir <- "/Volumes/WD_D/gufei/monkey_data/yuanliu/merge2monkey"
# function to plot tree
tree_plot <- function(model,color_list,title){
    rpart.plot(model,
        type = 1, # left and right split labels (see Figure 2)
        clip.right.labs = FALSE, # full right split labels
        extra = 104, # show nbr of obs and percentages (see Figure 3)
        under = FALSE, # position extra info _under_ the boxes
        tweak = 1, # tweak the text
        fallen.leaves = FALSE, # put leaves at the bottom of plot
        box.palette = color_list, # color of the boxes
        branch = .3, # branch lines with narrow shoulders and down slopes
        round = 0, # no rounding of node corners i.e. use rectangles
        leaf.round = 9, # round leaf nodes (for leaves, this supersedes the round arg)
        main = title, # title
        legend.x = 0,
        legend.y = 1,
        branch.col = "gray", # color of branch lines
        branch.lwd = 2 # line width of branch lines
    ) 
}
# recode odors
recode_odor <- function(power, tar) {
    # remove air
    power_noair <- power[odor != 6, ]
    # convert odor to factors
    power_noair[, odor := factor(odor, levels = as.character(1:5), labels = odors[1:5])]
    # frequency bands
    cutoff <- c(1, 4, 8, 13, 30, 80)
    freqbands_name <- c("delta", "theta", "alpha", "beta", "gamma")
    # dcast to frequencies
    power_by_time <- dcast(power_noair, roi + odor + time ~ freq, value.var = "power")
    for (i in 1:length(freqbands_name)) {
        # find freq index
        col <- which(freq >= cutoff[i] & freq < cutoff[i + 1]) + 3
        # average each frequency band
        power_by_time[, (freqbands_name[i]) := rowMeans(.SD), .SDcols = col]
    }
    # recode
    if (tar == "odor5") {
        power_by_time[, (tar) := odor]
    } else if (tar == "odor4") {
        power_by_time[, (tar) := car::recode(odor, 'c("Iso_l", "Iso_h") = "Iso"')]
        power_by_time[, (tar) := factor(odor4, levels = c("Ind", "Iso", "Peach", "Banana"))]
    } else if (tar == "valence") {
        power_by_time[, (tar) := car::recode(
            odor,'c("Ind", "Iso_l", "Iso_h") = "Neg"; c("Peach", "Banana") = "Pos"')]
        color_list <- color_list_all[c(1, 5)]
    } else if (tar == "intensity") {
        # select iso_l and iso_h
        power_by_time <- power_by_time[odor %in% c("Iso_l", "Iso_h"), ]
        power_by_time[, (tar) := factor(odor, levels = c("Iso_l", "Iso_h"), labels = c("Low", "High"))]
    } else if (tar == "indiso") {
        # select iso_l and iso_h
        power_by_time <- power_by_time[odor %in% c("Iso_l", "Iso_h","Ind"), ]
        power_by_time[, (tar) := car::recode(odor, 'c("Iso_l", "Iso_h") = "Iso"')]
    } else if (tar == "peaban") {
        # select iso_l and iso_h
        power_by_time <- power_by_time[odor %in% c("Peach", "Banana"), ]
        power_by_time[, (tar) := factor(odor, levels = c("Peach", "Banana"), labels = c("Pea", "Ban"))]
    }
    return(power_by_time)
}

color_tar <- function(color_list_all,tar){
    if (tar == "odor5") {
        color_list <- color_list_all
    } else if (tar == "odor4") {
        color_list <- color_list_all[-2]
    } else if (tar == "valence") {
        color_list <- color_list_all[c(1, 5)]
    } else if (tar == "intensity") {
        color_list <- color_list_all[c(2, 3)]
    }
}
# function to get classification results
class_results <- function(power_data,tar,av_freq=TRUE){
  # parallel
  future::plan(future::sequential)
  # multisession need to start a bunch of r sessions
  # if (future::supportsMulticore()) {
  #     future::plan(future::multicore)
  # } else {
  #     future::plan(future::multisession)
  # }
  power_by_time <- recode_odor(power_data, tar)
  # model by mlr3, select fearures
  task <- as_task_classif(power_by_time, target = tar)
  # Stratified resampling
  task$col_roles$stratum <- c("odor","roi")
  # Blocking times cannot combined with stratification
  # task$col_roles$group <- "time"
  if (av_freq) {
    feature_names <- freqbands_name
  } else {
    feature_names <- freqnames
  }
  task_freq <- task$clone()$select(feature_names)
  # rpart classifier
  # random forest with gini as importance measure
  # learner <- lrn("classif.randomForest", importance = "gini")
  learner <- lrn("classif.rpart")
  measure <- msr("classif.acc")
  ntime <- length(unique(power_by_time$time))
  nroi <- length(unique(power_by_time$roi))
  nodor <- length(unique(power_by_time$odor))
  # stratified cross validation
  # resampling  <-  rsmp("cv", folds = ntime)
  # custom cross validation
  f <- power_by_time$time
  resampling  <-  rsmp("custom_cv")
  resampling$instantiate(task_freq,f = f)
  rr <- resample(task_freq, learner, resampling, store_models = TRUE)
  
  # check resampling
  # task$strata
  # rr$resampling$instance
  # each fold has odor by roi samples (from random time points)
  # subset(rr$resampling$instance, fold==1)
  # autoplot(rr, measure = measure)
  
  # acc for each cv
  cv_acc <- rr$score(measure)$classif.acc
  # rr$aggregate(measure)
  importance <- rbindlist(lapply(rr$learners, function(x) data.table(t(x$importance()))),
                          use.names=TRUE,fill = TRUE)
  # replace na with 0
  # importance[is.na(importance)] <- 0
  setnafill(importance,fill=0)
  # deal with null (is_empty)
  if (dim(importance)[1]==0){
    importance <- data.table(matrix(data = 1/length(feature_names),
                                    nrow = ntime,ncol = length(feature_names)))
    setnames(importance,new = feature_names)
  }
  # predict labels
  response <- data.table(ids=rr$prediction()$row_ids,res = rr$prediction()$response)
  response <- response[order(ids),]
  results <- cbind(power_by_time[, .SD, .SDcols = c("roi", "time", tar)], response$res)
  setnames(results, 3:4, c("true", "response"))
  # add a column indicating target
  results[, `:=`(target = tar)]
  # calculate accuracy
  results <- results[, acc := ifelse(true == response, 1, 0)]
  return(list(resp = results, acc = cv_acc, import = importance))
}

# function to select roi
select_roi <- function(power_data,roi){
    if (roi == "HF") {
        # select rows Hi and S if roi is HF
        power_data <- power_data[roi %in% c("Hi", "S"), ]
    } else if (roi == "Amy") {
        # select rows except Hi and S
        power_data <- power_data[roi != "Hi" & roi != "S", ]
    }
    return(power_data)
}

# funtion to calculate average accuracy
avgacc <- function(results){
    return(results[, .(acc = mean(acc)), by = c("target","time","roi")])
}
```

# heatmap of monkey's zpower

```{r fig.height=4, fig.width=4}
# whether calculate zscore relative to air
cp_air  <- 1
for (m in monkeys){    
    pic_dir <- file.path(root_dir, 'pic/powerspec',m);
    # if cp_air is 1, add _air to pic_dir
    if (cp_air == 1) {
        pic_dir <- paste0(pic_dir, "_air")
    }
    # read zpower mat file
    data_pow <- readMat(file.path(pic_dir,'zpower_7s_1_80hz.mat'))
    # roi-odor condition-frequency bands
    zpower <- unlist(data_pow$zpower)
    rois <- unlist(data_pow$rois)
    freqbands <- paste0(c("1-4","4-8","8-13","13-30","30-50","50-80","30-80"),"Hz")
    # heatmap settings
    condition <- c(1:5)
    rownames(zpower) <- rois
    colnames(zpower) <- odors
    # color scale
    b <- seq(-0.1,0.1,length.out = 100)
    # plot heatmap and dendrogram for each frequency band
    for(freq in c(1:7)){
        pheatmap(zpower[, condition, freq],
        clustering_distance_rows = "correlation",
        clustering_distance_cols = "correlation",
        cellwidth = 15,cellheight = 15,breaks = b,
        color = colorRampPalette(rev(brewer.pal(n = 7, name = "RdBu")))(100),
        main = freqbands[freq],
        filename = file.path(pic_dir,paste0('heatmap_',freqbands[freq],'.pdf')))
    }
}
```

# load and store power data
```{r}
power_data <- list()
power_data_per <- list()
# for each monkey
for (m in monkeys) {       
    # colors for tree plot
    color_list_all <- list()
    c <- colors[1:5]
    c[2] <- "#858585"
    for (i in 1:5) {
        color_list_all[[i]] <- colorRampPalette(c("white", c[i]))(10)
    }
    # pic_dir
    pic_dir <- file.path(root_dir, "pic/pca_power/noair", m)
    # read zpower mat file
    data_pca <- readMat(file.path(pic_dir, "data_pca.mat"))
    # reorganize data from matlab cell to R
    roi_num  <- length(data_pca[[1]])/3
    rois <- unlist(data_pca[[1]][1:roi_num])
    # along 0 will bind in new dimension
    power <- abind(map(data_pca[[1]][(roi_num * 1 + 1):(roi_num * 2)], 1), along = 0)
    
    # bind list along the 3rd dimension
    # power <- abind(do.call(c, data_pca[[1]][(roi_num * 1 + 1):(roi_num * 2)]), along = 1)
    # power <- abind(map(data_pca[[1]][(roi_num * 1 + 1):(roi_num * 2)],1), along = 4)
    # labels <- abind(map(data_pca[[1]][(roi_num * 2 + 1):(roi_num * 3)],1),along = 0)

    # frequency
    freq <- 10^(seq(log10(1), log10(200), length.out = 51))
    freqnames <- sprintf("freq_%02d", c(1:dim(power)[4]))
    cutoff <- c(1, 4, 8, 13, 30, 80)
    freqbands_name <- c("delta", "theta", "alpha", "beta", "gamma")
    odor_num <- dim(power)[2]
    # set dimnames
    dimnames(power) <- list(c(1:roi_num), c(1:odor_num), seq(0, 3, 0.05), freqnames)
    # convert to data.table
    power <- as.data.table(power)
    names(power) <- c("roi", "odor", "time", "freq", "power")
    # convert roi and time to factors
    power[, time := factor(time, levels = as.character(seq(0, 3, 0.05)))]
    power[, roi := factor(roi, levels = as.character(1:roi_num), labels = rois)]
    # convert time and freq to numeric
    # power[,(c(3:4)):=lapply(.SD,as.numeric),.SDcols=c(3:4)]
    # store to list
    power_data[[m]] <- power
    
    # permutated data    
    data_pca_per <- readMat(file.path(pic_dir, "data_pca_per.mat"))
    per_num <- length(data_pca_per[[1]])
    power_data_per[[m]] <- data.table(matrix(ncol = 4+per_num, nrow = nrow(power)))
    power_data_per[[m]][,1:4] <- power[,1:4]
    # for each permutation
    for (per_i in 1:per_num) {
        p_i <- abind(map(data_pca_per[[1]][[per_i]][[1]][(roi_num * 1 + 1):(roi_num * 2)], 1), along = 0)
        # convert to data.table
        p_i <- as.data.table(p_i)
        power_data_per[[m]][,4+per_i] <- p_i[,5]
    }
    setnames(power_data_per[[m]],names(power_data_per[[m]]),
             c("roi", "odor", "time", "freq", paste0("power",1:per_num)))
}
# save power_data and power_data_per to Rdata
save(power_data, power_data_per, file = file.path(root_dir, "pic/pca_power/noair", paste0("Power_data_per",".Rdata")))
# settings for decodings
# use power for each frequency band
av_freq <- TRUE
# split test data set
test <- FALSE
# targets
tars <- c("odor5", "odor4", "valence", "intensity")
```

# decision tree based on time-frequency analysis

```{r eval=FALSE, fig.height=4, fig.width=4, include=FALSE}
# for each monkey
for (m in monkeys) {
    # set random seed
    set.seed(4869)   
    # load power data
    power <- power_data[[m]]        
    # store results
    datalist <- list()
    # for each coding methods
    for (tar in tars){
        # recode targets
        power_by_time <- recode_odor(power, tar)
        color_list <- color_tar(color_list_all, tar)
        # model by mlr3, select fearures
        task <- as_task_classif(power_by_time, target = tar)
        if (av_freq){
            task_freq <- task$clone()$select(freqbands_name)    
        } else {
            task_freq <- task$clone()$select(freqnames)
        }    
        # rpart classifier
        learner <- lrn("classif.rpart")
        measure = msr("classif.acc")
        # whether to test on test set
        if (test){
            split <- partition(task_freq, ratio = 55/61)
            train_idx <- split$train
            test_idx <- split$test
            learner$train(task_freq, row_ids = train_idx)
            prediction = learner$predict(task_freq, row_ids = test_idx)
            acc_test <- prediction$score(measure)
        } else {
            train_idx <- c(1:task_freq$nrow)
            learner$train(task_freq) 
            acc_test <- 0    
        }
        # test performance
        train_pre = learner$predict(task_freq, row_ids = train_idx)
        acc_train <- train_pre$score(measure)
        print(c(m, acc_train, acc_test))
        # relative importance
        print(c(learner$importance() / sum(learner$importance())))

        # get responses
        # select <- c("roi", "time", tar)
        # results <- cbind(power_by_time[,..select],train_pre$response)
        results <- cbind(power_by_time[, .SD, .SDcols = c("roi", "time", tar)], train_pre$response)
        setnames(results,3:4,c("true","response"))
        # add a column indicating target
        results[,`:=`(target = tar)]
        # calculate accuracy
        results <- results[,acc:=ifelse(true==response,1,0)]
        # save to list
        datalist[[tar]] <- results
        # average by odor and roi
        mean_acc <- results[target == tar, .(acc = mean(acc)), by = c("roi", "time")]
        # plot result matrix
        ggplot(mean_acc, aes(x = time, y = roi, fill = acc)) +
            geom_tile() + coord_equal(0.618*61/roi_num) +
            scale_fill_distiller(palette = "Greens",direction = 1,
            limits=c(0,1),breaks=seq(0,1,0.2)) +
            labs(title = paste(m, tar, sprintf("%.2f%%",100*acc_train), sep = "_")) +
            scale_x_discrete(breaks = seq(0,3,0.5))
        ggsave(file.path(pic_dir, paste0("Acc_", tar, ".pdf")), width = 5, height = 3)
        # save tree plot        
        # svg(file.path(pic_dir, "decision_tree.svg"))
        pdf(file.path(pic_dir, paste0("decision_tree_", tar, ".pdf")))
        title <- paste(m, tar, sprintf("%.2f%%", 100 * acc_train), sep = "_")
        tree_plot(learner$model,color_list,title)
        dev.off()
    }
    # bind all results
    results <- rbindlist(datalist,use.names=TRUE)
    # convert target to factor
    results[, target := factor(results$target, levels = tars)]    
    # plot averaged results
    # average by time
    mean_acc_time <- results[, .(acc = mean(acc)), by = c("target","time")]
    ggplot(mean_acc_time, aes(x = time, y = acc, group = target,color = target)) +
        geom_line() +
        labs(title = paste(m, sep = "_")) +
        scale_color_manual(values = cmap) +
        scale_x_discrete(expand = c(0, 0), breaks = seq(0, 3, 0.5)) +
        scale_y_continuous(expand = c(0, 0), limits = c(0, 1))
    ggsave(file.path(pic_dir, paste0("Acc_time", ".pdf")), width = 4, height = 2.5)
    # average by roi
    mean_acc_roi <- results[, .(acc = mean(acc)), by = c("target","roi")]
    # line plot
    ggplot(mean_acc_roi, aes(x = roi, y = acc, group = target,color = target)) +
        geom_line() +
        labs(title = paste(m, sep = "_")) +
        scale_color_manual(values = cmap) +
        scale_x_discrete(expand = c(0, 0)) +
        scale_y_continuous(expand = c(0, 0), limits = c(0, 1))
    ggsave(file.path(pic_dir, paste0("Acc_roi", ".pdf")), width = 5, height = 2.5)
}
```

# plot distance results

```{r eval=FALSE, include=FALSE}
dis_data <- list()
# for each monkey
for (m in monkeys) {  
    # pic_dir
    pic_dir <- file.path(root_dir, "pic/pca_power/noair", m)
    # read zpower mat file
    data_pca <- readMat(file.path(pic_dir, "distance_by_time.mat"))
    # reorganize data from matlab cell to R
    rois <- unlist(data_pca$rois)
    roi_num  <- length(rois)
    # along 0 will bind in new dimension
    distance <- abind(map(data_pca$dis.time, 1), along = 0)
    # set dimnames
    dimnames(distance) <- list(c(1:roi_num), seq(0, 3, 0.05), tars)
    # convert to data.table
    distance <- as.data.table(distance)
    setnames(distance,c("roi", "time", "target","dis"))
    # convert roi and time and target to factors
    distance[, time := factor(time, levels = as.character(seq(0, 3, 0.05)))]
    distance[, roi := factor(roi, levels = as.character(1:roi_num), labels = rois)]
    distance[, target := factor(target, levels = tars)]
    # store to list
    dis_data[[m]] <- distance
    # xlim for time
    time_up <- 1.2
    xrange <- c(1, time_up/0.05+1)
    # plot distance
    for (tar in tars){
        # average by odor and roi
        mean_dis <- distance[target == tar, .(dis = mean(dis)), by = c("roi", "time")]
        # plot result matrix
        ggplot(mean_dis, aes(x = time, y = roi, fill = dis)) +
            geom_tile() +
            coord_equal(0.618 * 61 / roi_num) +
            scale_fill_distiller(palette = "Greens", direction = 1) +
            labs(title = paste(m, tar,"distance", sep = "_")) +
            scale_x_discrete(breaks = seq(0, 3, 0.5))
        ggsave(file.path(pic_dir, paste0("Dis_", tar, ".pdf")), width = 5, height = 3)
    }
    # average by time
    mean_dis_time <- distance[, .(dis = mean(dis)), by = c("target", "time")]
    ggplot(mean_dis_time, aes(x = time, y = dis, group = target, color = target)) +
        geom_line() +
        labs(title = paste(m, sep = "_")) +
        scale_color_manual(values = cmap) +
        coord_cartesian(xlim = xrange)+
        scale_x_discrete(expand = c(0, 0), breaks = seq(0, time_up, 0.5)) +
        scale_y_continuous(expand = c(0, 0))
    ggsave(file.path(pic_dir, paste0("Dis_time", ".pdf")), width = 4, height = 2.5)
    # average by roi
    mean_dis_roi <- distance[, .(dis = mean(dis)), by = c("target", "roi")]
    # change roi levels
    mean_dis_roi <- mean_dis_roi[, roi := factor(roi, levels = roi_level)]
    # line plot
    # ggplot(mean_dis_roi, aes(x = roi, y = dis, group = target, color = target)) +
    #     geom_line() +
    #     labs(title = paste(m, sep = "_")) +
    #     scale_color_manual(values = cmap) +
    #     scale_x_discrete(expand = c(0, 0)) +
    #     scale_y_continuous(expand = c(0, 0))
    # ggsave(file.path(pic_dir, paste0("Dis_roi", ".pdf")), width = 5, height = 2.5)
    # heatmap
    ggplot(mean_dis_roi, aes(x = roi, y = target, fill = dis)) +
        geom_tile() +
        scale_fill_gradient(low = "white", high = "red") +
        labs(title = paste(m,sep = "_")) +
        guides(size="none")#+ removing legend for `fill`
        # geom_text(aes(label = round(dis,2), size = 5, vjust = 0.5), color = "black") 
    ggsave(file.path(pic_dir, paste0("Dis_roi_heat", ".pdf")), width = 5, height = 3)
}
```

# other decoding methods

## 2monkey

Train model on 2monkey and test on monkey RM033 and RM035 separately.

```{r eval=FALSE, include=FALSE}
m  <- "2monkey"
# for each coding methods
for (tar in tars){
    power_by_time <- recode_odor(power_data[[m]], tar)
    power_by_time1 <- recode_odor(power_data[["RM033"]], tar)
    power_by_time2 <- recode_odor(power_data[["RM035"]], tar)
    # model by mlr3, select fearures
    task <- as_task_classif(power_by_time, target = tar)
    task1 <- as_task_classif(power_by_time1, target = tar)
    task2 <- as_task_classif(power_by_time2, target = tar)
    if (av_freq) {
        task_freq <- task$clone()$select(freqbands_name)
        task_freq1 <- task1$clone()$select(freqbands_name)
        task_freq2 <- task2$clone()$select(freqbands_name)
    } else {
        task_freq <- task$clone()$select(freqnames)
        task_freq1 <- task1$clone()$select(freqnames)
        task_freq2 <- task2$clone()$select(freqnames)
    }
    # rpart classifier
    learner <- lrn("classif.rpart")
    measure <- msr("classif.acc")
    # whether to test on test set
    if (test) {
        split <- partition(task_freq, ratio = 55 / 61)
        train_idx <- split$train
        test_idx <- split$test
        learner$train(task_freq, row_ids = train_idx)
        prediction = learner$predict(task_freq, row_ids = test_idx)
        acc_test <- prediction$score(measure)
    } else {
        train_idx <- c(1:task_freq$nrow)
        learner$train(task_freq)
        acc_test <- 0
    }
    # test performance
    train_pre <- learner$predict(task_freq, row_ids = train_idx)
    test_33 <- learner$predict(task_freq1)
    test_35 <- learner$predict(task_freq2)
    acc_train <- train_pre$score(measure)
    print(c(m, acc_train, test_33$score(measure), test_35$score(measure)))
    # relative importance
    print(c(learner$importance()/sum(learner$importance())))

    # save tree plot
    color_list <- color_tar(color_list_all, tar)
    # svg(file.path(pic_dir, "decision_tree.svg"))
    # pdf(file.path(pic_dir, paste0("decision_tree_", tar, ".pdf")))
    title <- paste(m, tar, sprintf("%.2f%%", 100 * acc_train), sep = "_")
    tree_plot(learner$model, color_list, title)
    # dev.off()
}
```

## combine data from 2 monkeys

Combine data from monkey RM033 and RM035, tunning parameters and train model, then caculate accuracy for monkey RM033 and RM035 separately.

```{r eval=FALSE, include=FALSE}
# for each monkey
# for (m in monkeys) {
    # load power data
    m  <- "b2monkey"
    # power <- rbind(cbind(power_data[["RM033"]], rep("RM033", nrow(power_data[["RM033"]]))),
                    # cbind(power_data[["RM035"]], rep("RM035", nrow(power_data[["RM035"]]))))
    # for each coding methods
    for (tar in tars){
        power_by_time1 <- recode_odor(power_data[["RM033"]],tar)
        power_by_time2 <- recode_odor(power_data[["RM035"]],tar)
        power_by_time <- rbind(cbind(power_by_time1,rep("RM033",nrow(power_by_time1))),
                               cbind(power_by_time2,rep("RM035",nrow(power_by_time2))))
        setnames(power_by_time, "V2", "monkey")
        # model by mlr3, select fearures
        task <- as_task_classif(power_by_time, target = tar)
        if (av_freq) {
            task_freq <- task$clone()$select(freqbands_name)
        } else {
            task_freq <- task$clone()$select(freqnames)
        }
        # rpart classifier
        learner <- lrn("classif.rpart")
        measure <- msr("classif.acc")
        # tunning parameters
        search_space <- ps(
            cp = p_dbl(lower = 0.001, upper = 0.1),
            minsplit = p_int(lower = 1, upper = 10)
        )
        hout <- rsmp("holdout")
        evals20 <- trm("evals", n_evals = 20)
        instance <- TuningInstanceSingleCrit$new(
            task = task_freq,
            learner = learner,
            resampling = hout,
            measure = measure,
            search_space = search_space,
            terminator = evals20
        )
        tuner <- tnr("grid_search", resolution = 5)
        tuner$optimize(instance)
        learner$param_set$values <- instance$result_learner_param_vals
        # whether to test on test set
        if (test) {
            split <- partition(task_freq, ratio = 55 / 61)
            train_idx <- split$train
            test_idx <- split$test
            learner$train(task_freq, row_ids = train_idx)
            prediction = learner$predict(task_freq, row_ids = test_idx)
            acc_test <- prediction$score(measure)
        } else {
            train_idx <- c(1:task_freq$nrow)
            learner$train(task_freq)
            acc_test <- 0
        }
        # test performance
        train_pre = learner$predict(task_freq, row_ids = train_idx)
        acc_train <- train_pre$score(measure)
        print(c(m, acc_train, acc_test))
        # relative importance
        print(c(learner$importance()/sum(learner$importance())))

        # get responses
        results <- cbind(power_by_time[, .SD, .SDcols = c("monkey", "time", tar)], train_pre$response)
        setnames(results, 3:4, c("true", "response"))
        # add a column indicating target
        results[, `:=`(target = tar)]
        # calculate accuracy
        results <- results[, acc := ifelse(true == response, 1, 0)]
        # average by monkey
        print(results[target == tar, .(acc = mean(acc)), by = c("monkey")])
        # save tree plot
        color_list <- color_tar(color_list_all, tar)
        # svg(file.path(pic_dir, "decision_tree.svg"))
        pdf(file.path(pic_dir, paste0("b2monkey_treetun_", tar, ".pdf")))
        title <- paste(m, tar, sprintf("%.2f%%", 100 * acc_train), sep = "_")
        tree_plot(learner$model, color_list, title)
        dev.off()
    }
# }
```

## test cross validation 
```{r fig.height=2, fig.width=3}
# load data
load(file.path(root_dir, "pic/pca_power/noair", paste0("Power_data_per",".Rdata")))
# record processing time
ptm <- proc.time()
monkeys  <- c("RM033", "RM035", "2monkey")
results <- list()
results_per <- list()
tars <- c("odor5", "odor4", "valence", "intensity","indiso","peaban")
# tars <- c("indiso","peaban")
roiselect <- c("All","Amy","HF")
for (roi in roiselect){
    set.seed(823)
    # load(file.path(root_dir, "pic/pca_power/noair", paste0("Results_tree_", roi, ".Rdata")))
    for (m in monkeys) {
        # permutation data for current monkey
        power_data_per_m <- power_data_per[[m]]
        # for each coding methods
        for (tar in tars){
        # true results
        results[[m]][[tar]] <- class_results(select_roi(power_data[[m]],roi),tar,av_freq)
        # permutation results in parallel
        cluster <- parallel::makeCluster(20, type = "FORK")
        doParallel::registerDoParallel(cl = cluster)
        # doparalell
        results_per[[m]][[tar]] <- foreach (per_i = 1:per_num) %dopar% {
            power_per <- power_data_per_m[,.SD,.SDcols=c(1:4,per_i+4)]
            setnames(power_per,paste0("power",per_i),"power")
            class_results(select_roi(power_per,roi),tar,av_freq)
        }
        # stop cluster
        parallel::stopCluster(cl = cluster)
        }
    }
    proc.time() - ptm
    # save results and results_per to Rdata
    save(results, results_per, file = file.path(root_dir, "pic/pca_power/noair", paste0("Results_tree_", roi, ".Rdata")))
}
```

## Plot results
```{r fig.height=2, fig.width=3}
roiselect <- c("All","Amy","HF")
for (roi in roiselect){
    # load results and results_per
    load(file.path(root_dir, "pic/pca_power/noair", paste0("Results_tree_", roi, ".Rdata")))
    # average results
    impt_results <- list()
    resp_results <- list()
    for (m in monkeys) {
        pic_dir <- file.path(root_dir, 'pic/pca_power/noair',m);
        for (tar in tars){
        # extract list of accs
        accs_per <- map_depth(results_per[[m]][[tar]], 1, "acc")
        accs_tru <- results[[m]][[tar]][["acc"]]
        # t-test on 61 cv
        t.test(Reduce("+", accs_per) / length(accs_per), accs_tru, var.equal = T)
        # mean acc across 61 cvs for each permutation
        acc_per <- data.frame(acc = sapply(accs_per,mean))
        # 95% percentile
        cri <- quantile(acc_per$acc,0.95)
        # actual acc
        tru <- mean(accs_tru)
        # mean(acc_per<=tru)
        # histogram
        psize <- 2
        xrange <- c(floor(min(acc_per)*100)/100,ceiling(max(acc_per,tru)*100)/100)
        ggplot(acc_per,aes(x = acc))+
            geom_histogram(bins = 50,fill="#4d9dd4")+
            # plot p=0.95
            geom_vline(xintercept = cri,size=0.5,linetype = "dashed", color = "black")+
            geom_point(x=tru,y=psize*2,size=psize,color="red")+
            scale_y_continuous(expand = c(0,0))+
            scale_x_continuous(expand = c(0,0))+
            coord_cartesian(xlim = xrange)+
            labs(x="Accuracy",y="Count",title = paste(m,tar,sep = "_"))
        ggsave(file.path(pic_dir, paste0("Per_acc_", tar, '_', roi, ".pdf")), width = 3, height = 2)
        
        # collect importance
        impts_per <- map_depth(results_per[[m]][[tar]], 1, "import")
        impts_tru <- results[[m]][[tar]][["import"]]
        
        # divide by the sum of each row
        # impts_tru <- impts_tru[,.SD/rowSums(.SD)]
        # impts_per <- lapply(impts_per,function(x) x[,.SD/rowSums(.SD)])
        
        # mean importance for each permutation
        impt_per <- lapply(impts_per,function(x) as.list(colMeans(x)))
        # set use.names=TRUE because the order are not the same
        # impt_per <- rbindlist(impts_per,use.names=TRUE,fill = TRUE)
        impt_per <- rbindlist(impt_per,use.names=TRUE,fill = TRUE)
        setnafill(impt_per,fill=0)
        # 95% percentile
        cri <- apply(impt_per,2, quantile, c(0.025,0.95,0.975))
        m_impt <- apply(impt_per,2, mean)
        # actual importance
        tru <- apply(impts_tru, 2, mean)
        # combine
        cb_impt <- rbind(data.table(t(m_impt)),data.table(cri),data.table(t(tru)))
        labels <- c("per_mean","2.5%","95%","97.5%","true")
        target <- rep(tar,times=nrow(cb_impt))
        cb_impt <- cbind(cb_impt[,.SD/rowSums(.SD)],labels,target)
        impt_results[[m]][[tar]] <- cb_impt
        
        # collect responses
        resp_per <- map_depth(results_per[[m]][[tar]], 1, "resp")
        resp_tru <- results[[m]][[tar]][["resp"]]
        # mean respnses for each permutation
        resp_per <- lapply(resp_per,avgacc)
        # set use.names=TRUE because the order are not the same
        resp_per <- rbindlist(resp_per,use.names=TRUE,fill = TRUE)
        # 95% percentile
        # cri <- resp_per[, .(acc = quantile(acc,0.95)), by = c("target","time","roi")]
        cri <- resp_per[, .(acc = Rmisc::CI(acc,0.95)[1]), by = c("target","time","roi")]
        m_resp <- resp_per[, .(acc = mean(acc)), by = c("target","time","roi")]
        # actual importance
        tru <- resp_tru[, .(acc = mean(acc)), by = c("target","time","roi")]
        # combine
        cb_resp <- rbind(cbind(m_resp,rep("per_mean",times=nrow(m_resp))),
                         cbind(cri,rep("95%",times=nrow(m_resp))),
                         cbind(tru,rep("true",times=nrow(m_resp))))
        setnames(cb_resp,"V2","labels")
        resp_results[[m]][[tar]] <- cb_resp
        }
        
        # plot importance
        data_impt <- rbindlist(impt_results[[m]],use.names=TRUE)
        data_impt <- melt(data_impt, id = 6:7,variable.name="frequency", value.name = "importance")
        # change frequency labels and target to factors
        data_impt[,frequency:=factor(frequency,levels = c("delta", "theta", "alpha", "beta", "gamma"))]
        data_impt[,labels:=factor(labels,levels = c("true","95%","per_mean","2.5%","97.5%"))]
        data_impt[,target:=factor(target,levels = tars)]
        # line plot
        # ggplot(data_impt[labels%in%c("true","95%"),],aes(x=frequency,y=importance))+
        # geom_line(aes(group=interaction(labels,target),linetype=labels,color=target))+
        # scale_color_manual(values = cmap) +
        # labs(title = paste(m))
        
        # matrix plot
        # dcast data_impt change labels to columns
        data_impt <- dcast(data_impt, target + frequency ~ labels, value.var = "importance")
        # if true larger than 95% add a column of *
        data_impt[,plabels:=ifelse(true>`95%`,"*","")]
        ggplot(data_impt, aes(x = frequency, y = target, fill = true)) +
            geom_tile() +
            scale_fill_gradient(low = "white", high = "red") +
            labs(title = paste(m, roi, sep = "_")) +
            guides(size="none") + # removing legend for `fill`  
            theme(axis.text.x = element_text(angle = 45, hjust = 1))+
            geom_text(aes(label = plabels, size = 5, vjust = 0.5), color = "black") # printing values
        ggsave(file.path(pic_dir, paste0("Per_impt_", roi, ".pdf")), width = 3.5, height = 2) 
        
        # plot acc for each roi and time
        data_acc <- rbindlist(resp_results[[m]],use.names=TRUE)
        # convert target to factor
        data_acc[, target := factor(data_acc$target, levels = tars)]
        data_acc <- data_acc[target %in% tars[1:4], ]
        # plot averaged results
        # average by time
        mean_acc_time <- data_acc[, .(acc = mean(acc)), by = c("target","time","labels")]
        mean_acc_time[,labels:=factor(labels,levels = c("true","95%","per_mean"))]
        ggplot(mean_acc_time[labels%in%c("true","95%"),],
               aes(x = time, y = acc, group = interaction(labels,target),color = target)) +
            geom_line(aes(linetype = labels)) +
            labs(title = paste(m, roi, sep = "_")) +
            scale_color_manual(values = cmap) +
            scale_x_discrete(expand = c(0, 0), breaks = seq(0, 3, 0.5)) +
            scale_y_continuous(expand = c(0, 0), limits = c(0, 1))
        ggsave(file.path(pic_dir, paste0("Acc_time", roi, ".pdf")), width = 4, height = 2.5)
        # average by roi
        mean_acc_roi <- data_acc[, .(acc = mean(acc)), by = c("target","roi","labels")]
        mean_acc_roi[,labels:=factor(labels,levels = c("true","95%","per_mean"))]
        ggplot(mean_acc_roi[labels%in%c("true","95%"),],
               aes(x = roi, y = acc, group = interaction(labels,target),color = target)) +
            geom_line(aes(linetype = labels)) +
            labs(title = paste(m, roi, sep = "_")) +
            scale_color_manual(values = cmap) +
            scale_y_continuous(expand = c(0, 0), limits = c(0, 1))
        ggsave(file.path(pic_dir, paste0("Acc_roi", roi, ".pdf")), width = 4, height = 2.5)
        
    }
}
```

## test pipeline
```{r eval=FALSE, include=FALSE}
# show operators
oper <- as.data.table(mlr_pipeops)

```